Supplementary Information for 'Detecting' Manuscript

### 2023-07-26 SI_draft.Rmd
minor chnages to SI and re-knit

The number of observations in our simulations may bias the results. Therefore, we repeated the simulations described in the main, but varied the number of body size values sampled. We tested values of $n = 200, 500, 999, 5000, 10 000$. All other parameters of our simulations were kept the same as the simulations presented in the main text.

@@

![Figure S1. Absolute deviation in estimate from known value of $\lambda$. Points are jittered horizontally for visualization, and are deviations for each simulated replicate (n = 1000) across varying sample sizes of body size values. Lines are the average absolute deviation from the estimate. Colors indicate which method was used to estimate $\lambda$.](figures/abs_dev_by_body_n.png)
```{r, echo=FALSE, results='asis', message=FALSE}
library(knitr)
table1 <- read_csv("tables/abs_dev_n_vary.csv") %>%
  mutate(diff_abs_mean = round(diff_abs_mean, 3),
         diff_abs_sd = round(diff_abs_sd, 3)) %>%
  rename(method = name,
         "mean abs diff"=diff_abs_mean,
         "SD abs diff"=diff_abs_sd)
kable(table1,
         caption = "Table S1. Deviation of estimates across methods for different sample sizes of body values (body_n). The mean and standard deviation for each row (mean abs diff and sd abs diff, respectively) in the table are calculated across all replicates for each value of lambda (1000 reps * 5 lambda values = 5000 values.",
      padding = 10)
```

@@

```{r, echo=FALSE, results='asis', message=FALSE}
library(knitr)
table2 <- read_csv("tables/si_table2.csv") %>%
  mutate(diff_abs_mean = round(diff_abs_mean, 3),
         diff_abs_sd = round(diff_abs_sd, 3)) %>%
  rename(method = name,
         "mean abs diff"=diff_abs_mean,
         "SD abs diff"=diff_abs_sd)
kable(table2,
         caption = "Table S2. Deviation of estimates across methods when the values of the hypothetical gradient and the range of body sizes are changed.")
```

>>>>

The number of observations in our simulations may bias the results. Therefore, we repeated the simulations described in the main, but varied the number of body size values sampled. We tested values of $n = (200,~500,~999,~5000,~10~000)$. All other parameters of our simulations were kept the same as the simulations presented in the main text.

@@

![Figure S1. Absolute deviation in estimate from known value of $\lambda$. Points are jittered horizontally for visualization, and are deviations for each simulated replicate (n = 1000) across varying sample sizes of body size values. Lines are the average absolute deviation from the estimate. Colors indicate which method was used to estimate $\lambda$.](figures/abs_dev_by_body_n.png)
```{r, echo=FALSE, results='asis', message=FALSE}
library(knitr)
table1 <- read_csv("tables/abs_dev_n_vary.csv") %>%
  mutate(diff_abs_mean = round(diff_abs_mean, 3),
         diff_abs_sd = round(diff_abs_sd, 3)) %>%
  rename(method = name,
         "Body sample size" = body_n,
         "mean abs diff"=diff_abs_mean,
         "SD abs diff"=diff_abs_sd)
kable(table1,
         caption = "Table S1. Deviation of estimates across methods for different sample sizes of body size values. The mean and standard deviation for each row (mean abs diff and sd abs diff, respectively) in the table are calculated across all replicates for each value of lambda (1000 reps * 5 lambda values = 5000 values.",
      padding = 10)
```

@@

```{r, echo=FALSE, results='asis', message=FALSE}
library(knitr)
table2 <- read_csv("tables/si_table2.csv") %>%
  mutate(diff_abs_mean = round(diff_abs_mean, 3),
         diff_abs_sd = round(diff_abs_sd, 3)) %>%
  rename(method = name,
         "mean abs diff"=diff_abs_mean,
         "SD abs diff"=diff_abs_sd)
kable(table2,
         caption = "Table S2. Deviation of estimates across methods when the values of the hypothetical gradient (large x) and the range of body sizes (small m) are changed.")
```
